---
title: "Maternal_risk"
output: html_document
date: "2022-10-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Sources**

https://archive.ics.uci.edu/ml/datasets/Maternal+Health+Risk+Data+Set

Data has been collected from different hospitals, community clinics, maternal health cares from the rural areas of Bangladesh through the IoT based risk monitoring system.
Marzia Ahmed Email: ahmed.marzia32 ‘@’ gmail.com Institution: Daffodil International University, Dhaka, Bangladesh.

**About**

Data which provides information about significant risk factors for maternal mortality.

**Attribute Information:**

a)	Age: Any ages in years when a woman during pregnant.

b)	SBP: Systolic (Upper value) of Blood Pressure in mmHg, another significant attribute during pregnancy.

c)	DBP: Diastolic (Lower value) of Blood Pressure in mmHg, another significant attribute during pregnancy.

d)	BS: Blood glucose levels is in terms of a molar concentration, mmol/L.

e)	Temp: Temprature of body.

f)	HRate: Heart Rate of a normal resting heart rate in beats per minute.

g)	class: Predicted Risk Intensity Level during pregnancy considering the previous attribute.


## Attributes Details


```{r r1}
library(readxl)
library(moments)

risk <- read_xlsx("Health_Risk.xlsx")
class0 <- subset(risk,class=='low risk')
class1 <- subset(risk,class=='mid risk')
class2 <- subset(risk,class=='high risk')
options(digits = 2)
summary(risk)
```

**1) Age**

```{r r2,figures-side, fig.show='hold',out.width="25%"}
age0<-class0$Age
hist(age0, main= "Histogram for class 0")
age1<-class1$Age
hist(age1, main= "Histogram for class 1")
age2<-class2$Age
hist(age2, main= "Histogram for class 2")
age<-risk$Age
hist(age, main= "Histogram for all classes")
```


**2) SBP**

```{r r3,figures-side, fig.show='hold',out.width="25%"}
sbp0<-class0$SBP
hist(sbp0, main= "Histogram for class 0")
sbp1<-class1$SBP
hist(sbp1, main= "Histogram for class 1")
sbp2<-class2$SBP
hist(sbp2, main= "Histogram for class 2")
sbp<-risk$SBP
hist(sbp, main= "Histogram for all classes")
```


**3) DBP**

```{r r4,figures-side, fig.show='hold',out.width="25%"}
dbp0<-class0$DBP
hist(dbp0, main= "Histogram for class 0")
dbp1<-class1$DBP
hist(dbp1, main= "Histogram for class 1")
dbp2<-class2$DBP
hist(dbp2, main= "Histogram for class 2")
dbp<-risk$DBP
hist(dbp, main= "Histogram for all classes")
```


**4) BS**

```{r r5,figures-side, fig.show='hold',out.width="25%"}
bs0<-class0$BS
hist(bs0, main= "Histogram for class 0")
bs1<-class1$BS
hist(bs1, main= "Histogram for class 1")
bs2<-class2$BS
hist(bs2, main= "Histogram for class 2")
bs<-risk$BS
hist(bs, main= "Histogram for all classes")
```


**5) Temp**

```{r r6,figures-side, fig.show='hold',out.width="25%"}
temp0<-class0$Temp
hist(temp0, main= "Histogram for class 0")
temp1<-class1$Temp
hist(temp1, main= "Histogram for class 1")
temp2<-class2$Temp
hist(temp2, main= "Histogram for class 2")
temp<-risk$Temp
hist(temp, main= "Histogram for all classes")
```


**6) HRate**

```{r r7,figures-side, fig.show='hold',out.width="25%"}
HR0<-class0$HRate
hist(HR0, main= "Histogram for class 0")
HR1<-class1$HRate
hist(HR1, main= "Histogram for class 1")
HR2<-class2$HRate
hist(HR2, main= "Histogram for class 2")
HR<-risk$HRate
hist(HR, main= "Histogram for all classes")
```


## Correlation Matrix

**Class 0**

```{r}
options(digits = 2)
cor(class0[-7])
det(cov(class0[-7]))
```

**Class 1**

```{r}
options(digits = 2)
cor(class1[-7])
det(cov(class1[-7]))
```

**Class 2**

```{r}
options(digits = 2)
cor(class2[-7])
det(cov(class2[-7]))
```


**All Classes**

```{r}
options(digits = 2)
cor(risk[-7])
det(cov(risk[-7]))
```