---
title: "Diabetes"
output: html_document
date: "2022-10-6"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Source:**

https://archive.ics.uci.edu/ml/datasets/Early+stage+diabetes+risk+prediction+dataset.

**About**

Data has been collected using direct questionnaires from the patients of Sylhet Diabetes Hospital in Sylhet, Bangladesh and approved by a doctor.


**Attribute Information:**

a)	Age: 20-65

b)	Gender 1. Male, 0. Female

c)	PolyU: (Polyuria) 1. Yes, 0.No.

d)	PolyD: (Polydipsia) 1. Yes, 0.No.

e)	WLoss: (Sudden Weight Loss) 1. Yes, 0.No.

f)	Weak: (Weakness) 1. Yes, 0.No.

g)	PolyP: (Polyphagia) 1. Yes, 0.No.

h)	GThrush: (Genital Thrush) 1. Yes, 0.No.

i)	VB: (Visual Blurring) 1. Yes, 0.No.

j)	Itch: (Itching) 1. Yes, 0.No.

k)	Irritability: 1. Yes, 0.No.

l)	DHeal: (Delayed Healing) 1. Yes, 0.No.

m)	PP: (Partial Paresis) 1. Yes, 0.No.

n)	Stiff: (Muscle Stiffness) 1. Yes, 0.No.

o)	Alopecia: 1. Yes, 0.No.

p)	Obesity: 1. Yes, 0.No.

q)	class:  Positive, Negative.


**Contributors**

M M Faniqul Islam, Queen Mary University of London, United Kingdom m.islam ‘@’ smd17.qmul.ac.uk

Rahatara Ferdousi, Metropolitan University Sylhet, Bangladesh rahatara ‘@’ metrouni.edu.bd

Sadikur Rahman and Humayra, Metropolitan University Sylhet, Bangladesh rahmansadik004 ‘@’ gmail.com

Yasmin Bushra, Metropolitan University Sylhet, Bangladesh humayrabushra234 ‘@’ gmail.com


**Citation Request:**

Islam, MM Faniqul, et al. ‘Likelihood prediction of diabetes at early stage using data mining techniques.’ Computer Vision and Machine Intelligence in Medical Image Analysis. Springer, Singapore, 2020. 113-125. https://link.springer.com/chapter/10.1007/978-981-13-8798-2_12


## Attributes Details


```{r r1}
library(readxl)
library(dplyr)
library(ggplot2)

diabetes <- read_xlsx("D:/FOSSEE/Dataset/Data Set/Logical/Diabetes/Diabetes.xlsx")
class0 <- subset(diabetes,class=='Positive')
class1 <- subset(diabetes,class=='Negative')
```

**1) Age**

```{r r2,figures-side, fig.show='hold',out.width="33%"}
age0<-class0$Age
hist(age0, main= "Class 0", col = "blue")
age1<-class1$Age
hist(age1, main= "Class 1", col = "red")
age<-diabetes$Age
hist(age, main= "Both Classes", col = "green")
```

**2) Gender**

```{r r3,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(Gender)
ggplot(p, aes(x=(Gender),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(Gender)
ggplot(p, aes(x=(Gender),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(Gender)
ggplot(p, aes(x=(Gender),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**3) PolyU**

```{r r4,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(PolyU)
ggplot(p, aes(x=(PolyU),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(PolyU)
ggplot(p, aes(x=(PolyU),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(PolyU)
ggplot(p, aes(x=(PolyU),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**4) PolyD**

```{r r5,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(PolyD)
ggplot(p, aes(x=(PolyD),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(PolyD)
ggplot(p, aes(x=(PolyD),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(PolyD)
ggplot(p, aes(x=(PolyD),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```

**5) WLoss**

```{r r6,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(WLoss)
ggplot(p, aes(x=(WLoss),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(WLoss)
ggplot(p, aes(x=(WLoss),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(WLoss)
ggplot(p, aes(x=(WLoss),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**6) Weak**

```{r r7,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(Weak)
ggplot(p, aes(x=(Weak),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(Weak)
ggplot(p, aes(x=(Weak),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(Weak)
ggplot(p, aes(x=(Weak),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**7) PolyP**

```{r r8,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(PolyP)
ggplot(p, aes(x=(PolyP),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(PolyP)
ggplot(p, aes(x=(PolyP),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(PolyP)
ggplot(p, aes(x=(PolyP),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**8) GThrush**

```{r r9,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(GThrush)
ggplot(p, aes(x=(GThrush),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(GThrush)
ggplot(p, aes(x=(GThrush),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(GThrush)
ggplot(p, aes(x=(GThrush),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**9) VB**

```{r r10,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(VB)
ggplot(p, aes(x=(VB),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(VB)
ggplot(p, aes(x=(VB),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(VB)
ggplot(p, aes(x=(VB),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**10) Itch**

```{r r11,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(Itch)
ggplot(p, aes(x=(Itch),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(Itch)
ggplot(p, aes(x=(Itch),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(Itch)
ggplot(p, aes(x=(Itch),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**11) Irritability**

```{r r12,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(Irritability)
ggplot(p, aes(x=(Irritability),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(Irritability)
ggplot(p, aes(x=(Irritability),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(Irritability)
ggplot(p, aes(x=(Irritability),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**12) DHeal**

```{r r13,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(DHeal)
ggplot(p, aes(x=(DHeal),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(DHeal)
ggplot(p, aes(x=(DHeal),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(DHeal)
ggplot(p, aes(x=(DHeal),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**13) PP**

```{r r14,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(PP)
ggplot(p, aes(x=(PP),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(PP)
ggplot(p, aes(x=(PP),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(PP)
ggplot(p, aes(x=(PP),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**14) Stiff**

```{r r15,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(Stiff)
ggplot(p, aes(x=(Stiff),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(Stiff)
ggplot(p, aes(x=(Stiff),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(Stiff)
ggplot(p, aes(x=(Stiff),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**15) Alopecia**

```{r r16,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(Alopecia)
ggplot(p, aes(x=(Alopecia),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(Alopecia)
ggplot(p, aes(x=(Alopecia),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(Alopecia)
ggplot(p, aes(x=(Alopecia),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


**16) Obesity**

```{r r17,figures-side, fig.show='hold',out.width="33%"}
p <- class0 %>%
    count(Obesity)
ggplot(p, aes(x=(Obesity),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 0")

p <- class1 %>%
    count(Obesity)
ggplot(p, aes(x=(Obesity),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Class 1")

p <- diabetes %>%
    count(Obesity)
ggplot(p, aes(x=(Obesity),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)+
  ggtitle("Both Classes")
```


## Tables

**PolyU and PP**
```{r}
table(diabetes$PolyU,diabetes$PP)
```

**PolyU and PolyP**
```{r}
table(diabetes$PolyU,diabetes$PolyP)
```

**PolyU and PolyD**
```{r}
table(diabetes$PolyU,diabetes$PolyD)
```

**PolyU and WLoss**
```{r}
table(diabetes$PolyU,diabetes$WLoss)
```

**PolyD and WLoss**
```{r}
table(diabetes$PolyD,diabetes$WLoss)
```

**PolyD and PP**
```{r}
table(diabetes$PolyD, diabetes$PP)
```

**Stiff and VB**
```{r}
table(diabetes$Stiff, diabetes$VB)
```

**VB and PP**
```{r}
table(diabetes$VB, diabetes$PP)
```

**DHeal and Itch**
```{r}
table(diabetes$DHeal, diabetes$Itch)
```