---
title: "Wilt Data"
output: html_document
date: "2022-10-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Sources**

https://archive.ics.uci.edu/ml/datasets/wilt

Brian Johnson; Institute for Global Environmental Strategies; 2108-11 Kamiyamaguchi, Hayama, Kanagawa,240-0115 Japan; Email: Johnson ‘@’ iges.or.jp


**About**

This data set contains data from a remote sensing study by Johnson et al. (2013) that involved detecting diseased trees in Quickbird imagery.The data set consists of image segments, generated by segmenting the pansharpened image. The segments contain spectral information from the Quickbird multispectral image bands and texture information from the panchromatic (Pan) image band.

**Attribute Information:**

a)	class: ‘w’ (diseased trees), ‘n’ (all other land cover) 

b)	GLCM_Pan: GLCM mean texture (Pan band) 

c)	Mean_Green: Mean green value 

d)	Mean_Red: Mean red value 

e)	Mean_NIR: Mean NIR value 

f)	SD_Pan: Standard deviation (Pan band)

**Citation Request:**

Johnson, B., Tateishi, R., Hoan, N., 2013. A hybrid pansharpening approach and multiscale object-based image analysis for mapping diseased pine and oak trees. International Journal of Remote Sensing, 34 (20), 6969-6982.

## Attributes Details


```{r r1}
library(readxl)
library(moments)

wilt <- read_xlsx("Wilt_Dataset.xlsx")
class0 <- subset(wilt,class=='w')
class1<-subset(wilt,class=='n')
options(digits = 2)
summary(wilt)
```

**1) GLCM_Pan**

```{r r2,figures-side, fig.show='hold',out.width="33%"}
glcm0<-class0$GLCM_pan
hist(glcm0, main= "Histogram for class 0", col = "blue")
glcm1<-class1$GLCM_pan
hist(glcm1, main= "Histogram for class 1", col = "red")
glcm<-wilt$GLCM_pan
hist(glcm, main= "Histogram for both classes", col = "green")
```

**2) Green**

```{r r3,figures-side, fig.show='hold',out.width="33%"}
green0<-class0$Mean_Green
hist(green0, main= "Histogram for class 0", col = "blue")
green1<-class1$Mean_Green
hist(green1, main= "Histogram for class 1", col = "red")
green<-wilt$Mean_Green
hist(green, main= "Histogram for both classes", col = "green")
```

**3) Red**

```{r r4,figures-side, fig.show='hold',out.width="33%"}
red0<-class0$Mean_Red
hist(red0, main= "Histogram for class 0", col = "blue")
red1<-class1$Mean_Red
hist(red1, main= "Histogram for class 1", col = "red")
red<-wilt$Mean_Red
hist(red, main= "Histogram for both classes", col = "green")
```

**4) NIR**

```{r r5,figures-side, fig.show='hold',out.width="33%"}
nir0<-class0$Mean_NIR
hist(nir0, main= "Histogram for class 0", col = "blue")
nir1<-class1$Mean_NIR
hist(nir1, main= "Histogram for class 1", col = "red")
nir<-wilt$Mean_NIR
hist(nir, main= "Histogram for both classes", col = "green")
```

**5) Pan**

```{r r6,figures-side, fig.show='hold',out.width="33%"}
pan0<-class0$SD_pan
hist(pan0, main= "Histogram for class 0", col = "blue")
pan1<-class1$SD_pan
hist(pan1, main= "Histogram for class 1", col = "red")
pan<-wilt$SD_pan
hist(pan, main= "Histogram for both classes", col = "green")
```

## Correlation Matrix

**Class 0**

```{r}
options(digits = 2)
cor(class0[-1])
det(cor(class0[-1]))
```

**Class 1**

```{r}
options(digits = 2)
cor(class1[-1])
det(cor(class1[-1]))
```

**Both Classes**

```{r}
options(digits = 2)
cor(wilt[-1])
det(cor(wilt[-1]))
```

## Correlation Matrix

**Class 0**

```{r}
options(digits = 2)
cor(class0[-1])
cov(class0[-1])
det(cor(class0[-1]))
det(cov(class0[-1]))
eigen(cor(class0[-1]))
eigen(cov(class0[-1]))
```

**Class 1**

```{r}
options(digits = 2)
cor(class1[-1])
cov(class1[-1])
det(cor(class1[-1]))
det(cov(class1[-1]))
eigen(cor(class1[-1]))
eigen(cov(class1[-1]))
```
**Both Classes**

```{r}
options(digits = 2)
cor(wilt[-1])
det(cor(wilt[-1]))
det(cov(wilt[-1]))
```


```{r r6}
plot(1:5, eigen(cov(class1[-c(1)]))$values, cex=2)
points(1:5, eigen(cov(class0[-c(1)]))$values, col=2)
```