---
title: "Wholesale Customers Data"
output: html_document
date: "2022-10-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Sources**

https://archive.ics.uci.edu/ml/datasets/wholesale+customers
Margarida G. M. S. Cardoso, margarida.cardoso ‘@’ iscte.pt, ISCTE-IUL, Lisbon, Portugal

**Attribute Information:**

a)	fresh: annual spending on fresh products (Continuous)

b)	milk: annual spending on milk products (Continuous)

c)	grocery: annual spending on grocery products (Continuous)

d)	frozen: annual spending on frozen products (Continuous)

e)	DP: annual spending on Detergents and Paper products (Continuous)

f)	del: annual spending on and Delicatessen products (Continuous)

g)	region: customer Region - Lisnon, Oporto or Other (Nominal)

h)	class: customer Channel - (Hotel/Restaurant/Cafe) or (Retail channel)

**Citation Request:**

The data set is originated from a larger database referred on:

Abreu, N. (2011). Analise do perfil do cliente Recheio e desenvolvimento de um sistema promocional. Mestrado em Marketing, ISCTE-IUL, Lisbon

## Attributes Details


```{r r1}
library(readxl)
library(ggplot2)
library(dplyr)

wholesale <- read_xlsx("Wholesale_customers_data.xlsx")
options(digits = 2)
summary(wholesale)
```

**1) fresh**

```{r r2,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(wholesale,class==1)
fresh0<-class0$fresh
hist(fresh0, main= "Histogram for class 0", col = "blue")
class1<-subset(wholesale,class==2)
fresh1<-class1$fresh
hist(fresh1, main= "Histogram for class 1", col = "red")
fresh<-wholesale$fresh
hist(fresh, main= "Histogram for both classes", col = "green")
```

**2) milk**

```{r r3,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(wholesale,class==1)
milk0<-class0$milk
hist(milk0, main= "Histogram for class 0", col = "blue")
class1<-subset(wholesale,class==2)
milk1<-class1$milk
hist(milk1, main= "Histogram for class 1", col = "red")
milk<-wholesale$milk
hist(milk, main= "Histogram for both classes", col = "green")
```

**3) grocery**

```{r r4,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(wholesale,class==1)
grocery0<-class0$grocery
hist(grocery0, main= "Histogram for class 0", col = "blue")
class1<-subset(wholesale,class==2)
grocery1<-class1$grocery
hist(grocery1, main= "Histogram for class 1", col = "red")
grocery<-wholesale$grocery
hist(grocery, main= "Histogram for both classes", col = "green")
```

**4) frozen**

```{r r5,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(wholesale,class==1)
frozen0<-class0$frozen
hist(frozen0, main= "Histogram for class 0", col = "blue")
class1<-subset(wholesale,class==2)
frozen1<-class1$frozen
hist(frozen1, main= "Histogram for class 1", col = "red")
frozen<-wholesale$frozen
hist(frozen, main= "Histogram for both classes", col = "green")
```

**5) DP**

```{r r6,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(wholesale,class==1)
dp0<-class0$DP
hist(dp0, main= "Histogram for class 0", col = "blue")
class1<-subset(wholesale,class==2)
dp1<-class1$DP
hist(dp1, main= "Histogram for class 1", col = "red")
dp<-wholesale$DP
hist(dp, main= "Histogram for both classes", col = "green")
```

**6) del**

```{r r7,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(wholesale,class==1)
del0<-class0$del
hist(del0, main= "Histogram for class 0", col = "blue")
class1<-subset(wholesale,class==2)
del1<-class1$del
hist(del1, main= "Histogram for class 1", col = "red")
del<-wholesale$del
hist(del, main= "Histogram for both classes", col = "green")
```

**7) region**

```{r r8,figures-side, fig.show='hold',out.width="33%"}
class0 <- subset(wholesale,class==1)
class1<-subset(wholesale,class==2)

p <- class0 %>%
    count(region)
ggplot(p, aes(x=(region),y=n)) +
  geom_bar(fill = "blue", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)

p <- class1 %>%
    count(region)
ggplot(p, aes(x=(region),y=n)) +
  geom_bar(fill = "red", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)

p <- wholesale %>%
    count(region)
ggplot(p, aes(x=(region),y=n)) +
  geom_bar(fill = "green", stat = "identity")+
  geom_text(aes(label=n), vjust =-0.3)
```

## Correlation Matrix

**Class 1**

```{r}
options(digits = 2)
co0<-subset(wholesale,class==1)
cor(co0[-1])
cov(co0[-1])
det(cor(co0[-1]))
det(cov(co0[-1]))
eigen(cor(co0[-1]))
eigen(cov(co0[-1]))
```

**Class 2**

```{r}
options(digits = 2)
co1<-subset(wholesale,class==2)
cor(co1[-1])
cov(co1[-1])
det(cor(co1[-1]))
det(cov(co1[-1]))
eigen(cor(co1[-1]))
eigen(cov(co1[-1]))
```
**Both Classes**

```{r}
options(digits = 2)
cor(wholesale[-1])
det(cor(wholesale[-1]))
det(cov(wholesale[-1]))
```


```{r r6}
plot(1:7, eigen(cov(co1[-c(1)]))$values, cex=2)
points(1:7, eigen(cov(co0[-c(1)]))$values, col=2)
```